Adaptive broadcast tree for multicores

### 2013-07-24 paper.tex
Rerun of all (gruyere, gottardo, sbrinz, tomme, ziger) UMP breakdowns to refine models and all topologies with the new models

\paragraph{Atomic broadcast} An Atomic broadcasts is a broadcast
messaging protocol that is reliable in the sense that if a message is
received by one of the participating nodes, it is also received by all
other nodes. Furthermore, the order of messages as seen by all
participants is the same. Atomic broadcasts are frequently used to
implement higher-level distributed algorithms on top of it: examples
are replication such as state machine replication. As a first step, we
evaluate the performance of sending one message as a broadcast to all
nodes. Broadcasts are one of the most important communication
operations for parallel applications~\cite{Bruck1992}. \stefan{Database
  joins}.

@@

\stefan{Have not implemented this, but it might be interesting to try
  out later}

We discussed earlier in Section~\ref{sec:model} that
multicore machines are hierarchical.%

We divide the space into clusters. In every round, we further split up
all cluster into smaller clusters and connect them with the minimal
link.

We find this link by searching for links that have start and
end node in different regions of the most recent split. Out of these
links, we pick the cheapest ones. We ignore links whose start or end
node have a too high degree in the spanning tree already.

Assuming that the choice of node IDs represents the topology to some
extend, splitting them up into distinct clusters avoids contention, as
two separate sub-trees are processed in different areas of the
interconnect network.

Another idea is to employ clustering on NUMA domains such that every
NUMA domain corresponds to one cluster.

@@

\begin{figure}[htb]
  \centering
  \begin{tikzpicture}[scale=.35,transform shape]
    % Insert visualization
    \input{visu_only_mst}
  \end{tikzpicture}
  \caption{Visualization of operations for sending a message along the
    tree. Red boxes represent send operations, blue boxes represent
    receive operations and arrows messages sent between cores. The
    tree has been acquired using an MST algorithm.}
  \label{fig:mst_gruyere_operations}
\end{figure}

@@

\begin{figure}[htb]
  \centering
  \begin{tikzpicture}[scale=.35,transform shape]
    % Insert visualization
    \input{visu_mst_sort}
  \end{tikzpicture}
  \caption{Visualization of operations for sending a message along the
    tree. Red boxes represent send operations, blue boxes represent
    receive operations and arrows messages sent between cores. After
    running the MST algorithm, we optimize scheduling in every node to
    send messages in decreasing order of their latency.}
  \label{fig:mst_gruyere_operations_sorted}
\end{figure}

@@

\begin{table}[htb]
  \centering
  \begin{tabular}{lllll}
    \toprule
    topology & scheduling & time & factor & figure \\
    \midrule
    MST & naive                     & 241 & 1.00 & 
        \ref{fig:mst_gruyere_operations} \\
    MST & highest link weight first & 151 & 0.63 & 
        \ref{fig:mst_gruyere_operations_sorted} \\
    MST & longest path first        & 151 & 0.63 & 
        \stefan{? AFAIK, same as
        \ref{fig:mst_gruyere_operations_sorted} } \\
    hierarchical & highest link weight first & 151 & 0.63 &
        \ref{fig:visu_hierarchy} \\
    ring & highest link weight first & 181 & 0.75 &
        \ref{fig:visu_ring} \\
    \bottomrule
  \end{tabular}
  \caption{Simulation results for simplified machine model}
  \label{tab:sim_results}
\end{table}

@@

\begin{figure}[htb]
  \centering
  \begin{tikzpicture}[scale=.35,transform shape]
    % Insert visualization
    \input{visu_hierarchy}
  \end{tikzpicture}
  \caption{Visualization of hierarchical tree broadcast. A binary tree
    spans across NUMA nodes followed by sequential send operations
    within the NUMA node. %
    Red boxes represent send operations, blue boxes represent receive
    operations and arrows messages sent between cores.  }
  \label{fig:visu_hierarchy}
\end{figure}

\begin{figure}[htb]
  \centering
  \begin{tikzpicture}[scale=.35,transform shape]
    % Insert visualization
    \input{visu_ring}
  \end{tikzpicture}
  \caption{Visualization of ring based broadcast. Two rings
    spans across NUMA nodes followed by sequential send operations
    within the NUMA node. %
    Red boxes represent send operations, blue boxes represent receive
    operations and arrows messages sent between
    cores. \stefan{Scheduling is broken. If we want acks, we can only
      forward a message along the ring when all the local nodes
      acknowledge a message}}
  \label{fig:visu_ring}
\end{figure}

@@

\paragraph{Binary tree on sbrinz2}

Plot~\ref{pgfplot:201305101058} shows the time in cycles until a
message send from core $n$ is received back via the broadcast tree
show in Figure~\ref{fig:binary_tree_sbrinz2}. We were expecting
increasing cost with the depth of the tree. If a message is sent from
one of the leave nodes, it takes longer to receive this message back
on the tree.

The result is quite unexpected. We would expect nodes far down in the
tree to experience a longer waiting time for receiving own messages
back on the tree (due to more hops). This observation does not seem to
be true.

Lukas Humbel, who was also working on sbrinz1 was observing that the
Barrelfish core IDs might not properly correspond to physical core
IDs. This could explain the numbers we observe in our measurement.

\begin{figure}[htb]
  \centering
  \includegraphics[width=\linewidth]{binary_tree_sbrinz2}
  \caption{Binary tree for sbrinz2}
  \label{fig:binary_tree_sbrinz2}
\end{figure}

\begin{figure}
  \caption{Cost for receiving a message back on the tree. This is the
    time for which the send call needs to be blocked to retain atomic
    broadcast properties.}
  \label{pgfplot:201305101058}
  \begin{tikzpicture}
    \begin{axis}[%
        xlabel=sender core ID,%
        ylabel={Cost [cycles]}%
        ]
    \addplot[%
        color=red,%
        mark=x,%  
        error bars/y dir=both,%
        error bars/y explicit%
        ] coordinates {
      (1,276.1) +- (291.3,291.3)
      (2,876.1) +- (56.6,56.6)
      (3,863.0) +- (108.3,108.3)
      (4,899.7) +- (102.3,102.3)
      (5,893.5) +- (44.5,44.5)
      (6,880.5) +- (39.4,39.4)
      (7,520.9) +- (41.7,41.7)
      (8,171.9) +- (91.5,91.5)
      (9,155.7) +- (51.4,51.4)
      (10,174.6) +- (99.9,99.9)
      (11,175.1) +- (99.3,99.3)
      (12,154.5) +- (50.5,50.5)
      (13,176.8) +- (109.7,109.7)
      (14,173.1) +- (99.4,99.4)
      (15,150.4) +- (43.3,43.3)
    };
    \end{axis}
  \end{tikzpicture}
\end{figure}

\paragraph{Older numbers}

Plot~\ref{pgfplot:201303141819} shows the cost of flooding a sub-tree
(with the 50\% worst measurements dropped). The group communication is
based on a binary tree. Core 0 is the root, cores 1 and 2 are its
children etc.

The average cost is really high (probably a scheduling issue). But the
minimal numbers show what is possible. The numbers achieved are easily
explainable. The cost is increasing logarithmic with the number of
nodes reached by the broadcast (as expected). Every level in the tree
adds an additional 2500 to 3000 cycles to the tree. Node 0 takes
significantly longer. I don't know yet why that is.

\begin{figure}
  \caption{Execution time for a broadcast with ACK on gruyere. The
    cost is for execution for the sub-graph starting at the given
    node. Refer to Figure~\ref{fig:qrm_tree_gruyere} for a
    visualization of the broadcast tree used. }
  \label{pgfplot:201303141819}
  \begin{tikzpicture}
    \begin{axis}[
      xlabel=core id,
      scaled y ticks = false, % prevent 10^x stuff
      y tick label style={/pgf/number format/fixed},
      ylabel={cost for subtree [cycles]}]
    \addplot[
      color=red,
      very thin,
      mark=*,
      mark options={%
        scale=.4
      },
      error bars/y dir=both,
      error bars/y explicit] coordinates {
      (0,9932.3) +- (564.4,564.4)
      (1,8240.1) +- (298.5,298.5)
      (2,8259.6) +- (549.4,549.4)
      (3,6206.3) +- (225.1,225.1)
      (4,5914.9) +- (399.2,399.2)
      (5,6033.5) +- (462.2,462.2)
      (6,6070.4) +- (434.3,434.3)
      (7,4530.4) +- (188.6,188.6)
      (8,3163.4) +- (246.1,246.1)
      (9,3403.0) +- (285.3,285.3)
      (10,3650.7) +- (336.5,336.5)
      (11,3559.0) +- (318.8,318.8)
      (12,3558.1) +- (284.8,284.8)
      (13,3567.5) +- (304.5,304.5)
      (14,3476.3) +- (290.2,290.2)
      (15,2711.7) +- (151.9,151.9)
      (16,614.0) +- (17.5,17.5)
      (17,606.2) +- (17.3,17.3)
      (18,636.2) +- (72.5,72.5)
      (19,641.3) +- (46.3,46.3)
      (20,583.8) +- (46.7,46.7)
      (21,577.8) +- (38.3,38.3)
      (22,561.8) +- (18.1,18.1)
      (23,603.5) +- (56.6,56.6)
      (24,589.0) +- (33.4,33.4)
      (25,582.9) +- (33.2,33.2)
      (26,571.7) +- (16.3,16.3)
      (27,581.6) +- (36.6,36.6)
      (28,564.0) +- (16.4,16.4)
      (29,564.0) +- (20.8,20.8)
      (30,551.6) +- (13.0,13.0)
      (31,596.2) +- (51.4,51.4)
    };
    \end{axis}
  \end{tikzpicture}

\end{figure}

@@

\begin{appendices}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{UMP performance}

\input{graphs/ziger_ump_breakdown}

\subsection{Pairwise performance}

Figure~\ref{pgfplot:20130627} shows the UMP RTT time for each pair of
cores. The benchmark seems to be broken, since sending messages to
core 40 and higher is really expensive. On the other hand. Sending
messages from these cores back to cores with low IDs (which are on the
other end of the machine) seems unreasonably cheap.

What we would expect is a symmetric plot. Sending a message from core
$n$ to $m$ should be about equally expensive than sending a message
from $m$ to $n$.

\pgfplotsset{width=\linewidth}
\begin{figure}
  \caption{pair-wise latency for appenzeller}
  \label{pgfplot:20130627}
  \begin{tikzpicture}
    \begin{axis}[
      zlabel={cost [cycles]},
      xlabel={sending core},
      ylabel={receiving core},
      scaled z ticks = false,
      z tick label style={/pgf/number format/fixed}
      ]
    \addplot3[surf] file {measurements/appenzeller_pairwise_ump.dat};
    \end{axis}
  \end{tikzpicture}
\end{figure}

\pgfplotsset{width=\linewidth}
\begin{figure}
  \caption{pair-wise latency for gottardo}
  \label{pgfplot:20130627}
  \begin{tikzpicture}[scale=.75]
    \begin{axis}[scaled z ticks=false,z tick label style={/pgf/number format/fixed},zlabel={cost [cycles]},xlabel={sending core},ylabel={receiving core}]
    \addplot3[surf] file {measurements/gottardo_pairwise_ump.dat};
    \end{axis}
  \end{tikzpicture}
\end{figure}

\section{Shared memory performance}

Plot~\ref{pgfplot:201306191213} shows some measurements for using a
shared memory FIFO queue for communication. Core 0 sends message by
enqueuing them to the FIFO, while all other cores poll on the queue
for new messages.

The measurement assumes the tsc clocks to be synchronized. The queues
are also infinite. Messages are never garbage-collected.

\begin{figure}
  \caption{Shared memory FIFO performance on brie}
  \label{pgfplot:201306191213}
  \begin{tikzpicture}
    \begin{axis}[
      ybar,
      error bars/y dir=both,%
      error bars/y explicit,%
      xlabel=core,
      xtick={1,2,3},
      ylabel={cost [cycles]}]

    \addplot coordinates {
      (1,488.6) +- (32.1,32.1)
      (2,761.7) +- (124.1,124.1)
      (3,862.5) +- (118.3,118.3)
    };
    \end{axis}
  \end{tikzpicture}
\end{figure}

Plot~\ref{pgfplot:201306191238} shows the same experiment for tomme.

\begin{figure}
  \caption{Shared memory FIFO performance on tomme}
  \label{pgfplot:201306191238}
  \begin{tikzpicture}
    \begin{axis}[
      ybar,
      error bars/y dir=both,
      error bars/y explicit,
      xlabel=core,
      ylabel={Cost [cycles]}]
    \addplot coordinates {
      (1,417.6) +- (71.0,71.0)
      (2,776.2) +- (110.4,110.4)
      (3,774.6) +- (111.9,111.9)
      (4,648.0) +- (175.9,175.9)
      (5,551.2) +- (257.5,257.5)
      (6,652.6) +- (179.2,179.2)
      (7,688.6) +- (116.3,116.3)
      (8,691.2) +- (133.0,133.0)
      (9,721.6) +- (55.8,55.8)
      (10,633.8) +- (135.0,135.0)
      (11,673.8) +- (86.4,86.4)
      (12,705.0) +- (81.8,81.8)
      (13,612.6) +- (199.1,199.1)
      (14,699.2) +- (90.3,90.3)
      (15,691.6) +- (93.0,93.0)
    };
    \end{axis}
  \end{tikzpicture}
\end{figure}

Plot~\ref{pgfplot:201306191603} shows it for gruyere. These do not
make sense. The numbers are far too high, especially since gruyere is
supposed to be synchronized.

This suggest that my implementation is broken ..

\begin{figure}
  \caption{Plot}
  \label{pgfplot:201306191603}
  \begin{tikzpicture}
    \begin{axis}[
      ybar,
      error bars/y dir=both,
      error bars/y explicit,
      xlabel=FIXME,
      ylabel={Cost [cycles]}]
    \addplot coordinates {
      (1,2399.4) +- (3585.1,3585.1)
      (2,8924.9) +- (11981.8,11981.8)
      (3,4922.3) +- (4685.1,4685.1)
      (4,6638.2) +- (3521.0,3521.0)
      (5,5608.7) +- (4185.6,4185.6)
      (6,5337.5) +- (3846.6,3846.6)
      (7,5844.6) +- (2836.9,2836.9)
      (8,5089.0) +- (3135.3,3135.3)
      (9,5264.0) +- (3919.9,3919.9)
      (10,5711.7) +- (3793.0,3793.0)
      (11,5266.9) +- (3712.1,3712.1)
      (12,8197.6) +- (3819.3,3819.3)
      (13,8668.6) +- (3645.8,3645.8)
      (14,8923.8) +- (2964.8,2964.8)
      (15,7195.3) +- (2407.2,2407.2)
      (16,8176.2) +- (3185.2,3185.2)
      (17,8770.7) +- (3001.8,3001.8)
      (18,4171.5) +- (2011.4,2011.4)
      (19,8453.5) +- (3280.2,3280.2)
      (20,13695.1) +- (3137.6,3137.6)
      (21,13806.8) +- (2914.0,2914.0)
      (22,13692.4) +- (2730.3,2730.3)
      (23,14435.9) +- (2983.7,2983.7)
      (24,9797.6) +- (3821.4,3821.4)
      (25,8955.7) +- (4364.6,4364.6)
      (26,7929.3) +- (3493.3,3493.3)
      (27,11541.9) +- (3076.2,3076.2)
      (28,10851.3) +- (4241.4,4241.4)
      (29,8736.3) +- (3280.4,3280.4)
      (30,11648.2) +- (2969.7,2969.7)
      (31,7821.5) +- (2477.0,2477.0)
    };
    \end{axis}
  \end{tikzpicture}
\end{figure}

Plot~\ref{pgfplot:201306191624} shows the same with more
iterations. The result is not more stable than the one before,
though.

\begin{figure}
  \caption{Plot}
  \label{pgfplot:201306191624}
  \begin{tikzpicture}
    \begin{axis}[
      ybar,
      error bars/y dir=both,
      error bars/y explicit,
      xlabel=FIXME,
      ylabel={Cost [cycles]}]
    \addplot coordinates {
      (1,11197.7) +- (8150.8,8150.8)
      (2,10971.4) +- (6418.6,6418.6)
      (3,10364.3) +- (7409.8,7409.8)
      (4,9460.5) +- (6846.3,6846.3)
      (5,11629.7) +- (7938.9,7938.9)
      (6,12266.8) +- (8895.5,8895.5)
      (7,12313.0) +- (8030.9,8030.9)
      (8,13079.3) +- (7031.2,7031.2)
      (9,10919.1) +- (6272.3,6272.3)
      (10,4758.1) +- (3364.5,3364.5)
      (11,4093.8) +- (2121.7,2121.7)
      (12,10077.3) +- (1152.3,1152.3)
      (13,8632.7) +- (1601.4,1601.4)
      (14,6381.6) +- (1607.5,1607.5)
      (15,8215.2) +- (1799.2,1799.2)
      (16,6973.4) +- (1713.0,1713.0)
      (17,8631.0) +- (1750.3,1750.3)
      (18,13615.4) +- (2873.1,2873.1)
      (19,11311.9) +- (1996.6,1996.6)
      (20,17855.8) +- (2420.9,2420.9)
      (21,15193.0) +- (1923.7,1923.7)
      (22,18920.0) +- (2393.1,2393.1)
      (23,19870.6) +- (2618.8,2618.8)
      (24,17947.8) +- (4379.8,4379.8)
      (25,21783.5) +- (4202.5,4202.5)
      (26,24329.6) +- (3695.0,3695.0)
      (27,22965.0) +- (3667.8,3667.8)
      (28,20440.8) +- (4380.6,4380.6)
      (29,17405.7) +- (4385.3,4385.3)
      (30,19202.7) +- (4509.1,4509.1)
      (31,21855.2) +- (3850.9,3850.9)
    };
    \end{axis}
  \end{tikzpicture}
\end{figure}

\newpage
\input{measurements/gruyere_topologies}

Table~\ref{tab:ziger1} shows an overview of topologies for atomic
broadcast on \ziger. We compare these numbers to cost-estimations from
our simulator that incorporates detailed UMP breakdown measurements
done on the same machine. Our estimations are close to what we observe
when running on real hardware. In particular, the order of efficiency
of the topologies matches reality.

The only exception is sequential execution. Our simulator predicts
much worse performance than actually given by hardware. We believe the
cause for this could be hardware extensions (e.g.\ hardware broadcast
units or snooping).

What is particularly interesting is that a badly chosen tree with lots
of communication across NUMA nodes is actually worse than sequentially
sending messages.

\input{measurements/ziger1_topologies}
\input{measurements/sbrinz_topologies}
\input{measurements/appenzeller_topologies}

%\input{graphs/visall}

\end{appendices}

>>>>

\paragraph{Atomic broadcast} An Atomic broadcasts is a broadcast
messaging protocol that is reliable in the sense that if a message is
received by one of the participating nodes, it is also received by all
other nodes. Furthermore, the order of messages as seen by all
participants is the same. Messages are immutable, i.e.\ all receivers
read exactly the same message.

Atomic broadcasts are frequently used to implement higher-level
distributed algorithms on top of it: examples are replication such as
state machine replication. As a first step, we evaluate the
performance of sending one message as a broadcast to all
nodes. Broadcasts are one of the most important communication
operations for parallel applications~\cite{Bruck1992}.%
\stefan{Also: Database joins}.

@@

We discussed earlier in Section~\ref{sec:model} that
multicore machines are hierarchical. We discuss here a more
methodical approach for communication withing hybrid networks.

The idea is to find clusters of cores for whom shared memory
algorithms are more efficient then their message passing-based
counter-parts.

In a shared memory implementation, the cost of enqueueing a message to
a shared memory queue is $t_{write}$. The reads ideally (i.e.\ not
considering contention) happen in parallel, which means $t_{read}$
independent of how many clients read the data, but cause $n$-fault
traffic on the interconnect.

We now assume that the receiving cores shared a cache. Each message is
then available locally for further read operations by other cores
after the first core was issuing a read. This first read forces the
cache-coherency protocol to update (or pull) the message that was
invalidated by the sender write operation.

A shared memory implementation is more efficient for a group of cores
$c_1 \ldots c_n \in C$ if $t_{write} + t_{rem-read} +
(n-1)*t_{local-read}$ is smaller then the cost of sending a message
along the most efficient message-passing topology for this set of
cores.

\begin{algorithm}[htb]
  %%%%% 
  \SetCommentSty{textc}
  \SetKwFunction{sort}{sort} %
  \SetKwFunction{cost}{cost} %
  \SetKwFunction{pop}{pop} %
  \SetKwFunction{shortestmp}{shortest\_mp} %
  \SetKwFunction{costshm}{cost\_shm} %
  \SetKwFunction{cluster}{get\_cluster} %
  \SetKwFunction{icsend}{send} %
  %%%%
  \KwData{Edges E from model}
  %%%%%

  \While{True}{
    links $\leftarrow$ \sort{E}\;
    \Repeat{stderr small enough}{
      (start, end) = \pop{links}\;
      clusters += start, end\;
    }
    clusters $\leftarrow $ \cluster{}\;
    \eIf{\cost{\shortestmp{cores}} $<$ \costshm{cores}}{
      cores $\leftarrow$ cluster\;
    }{
      break \;
    }
  }
  \If{cores}{
    Compose algorithm
  }
  %%%%%
  \caption{Algorithm to find shared memory clusters}
  \label{algo:clustering}
\end{algorithm}

@@

@@

@@

\begin{table}[htb]
  \centering
  \begin{tabular}{lllll}
    \toprule
    topology & scheduling & time & factor & figure \\
    \midrule
    MST & naive                     & 241 & 1.00 & 
        \ref{fig:mst_gruyere_operations} \\
    MST & highest link weight first & 151 & 0.63 & 
        \ref{fig:mst_gruyere_operations_sorted} \\
    MST & longest path first        & 151 & 0.63 & 
        \stefan{? AFAIK, same as
        \ref{fig:mst_gruyere_operations_sorted} } \\
    hierarchical & highest link weight first & 151 & 0.63 & \\
    ring & highest link weight first & 181 & 0.75 & \\
    \bottomrule
  \end{tabular}
  \caption{Simulation results for simplified machine model}
  \label{tab:sim_results}
\end{table}

@@

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}

\input{measurements/gruyere_topologies}

Table~\ref{tab:gottardo} shows results for various atomic broadcasts
trees on real hardware as well as our simulator.

The simulator is not very accurate in this case due to the send time
measured being essentially zero on Intel machines. This measurement
does not consider the constant overhead in software for sending a
message that was not part of the original send benchmark.

We either need to send and receive benchmarks with the exact same
framework or measure the constant overhead and add it to the send
cost.

Sequentially sending messages is still expensive even though the send
itself is cheap on Intel machines. This is somewhat unexpected, as the
sender has very low overhead in sending all messages
itself. Sequentially sending all messages however induces several
expensive message transfers across NUMA nodes.

\input{measurements/gottardo_topologies}

\input{measurements/sbrinz_topologies}
\input{measurements/tomme_topologies}
\input{measurements/ziger_topologies}

### 2013-07-24 pitch.tex
Rerun of all (gruyere, gottardo, sbrinz, tomme, ziger) UMP breakdowns to refine models and all topologies with the new models

\paragraph{What do you want to enable?} 
Atomic broadcast for multicores. \stefan{Maybe even more high-level:
  Performance of distributed algorithms like replication that are
  built on top of AB}

\paragraph{What problem are you solving, and why is it hard?} 
Tuning of AB to machine characteristics. This is hard because
multicores are complex hierarchical system. Furthermore, there is a
huge variety of such machines with different characteristics
influencing performance.

@@

\paragraph{How will you go about it?}
Online measurements to augment Model \ska evaluation of different
implementations for machine (also combination of message-passing and
shared-memory) \ska pick best fit \ska auto-tune implementation

\paragraph{How will you know and show it works?}
Compare different AB implementations. Show that performance depends on
machine. Show that our evaluation picks the best one. Verify
performance benefit for high-level application.

@@

\paragraph{What is your hypothesis?}
We can do better with hybrid models. Automatic tuning achieves good
performance, without programmers having to deal with complex hardware details.

>>>>

\paragraph{What do you want to enable?} 
Efficient atomic broadcast for multicores. \stefan{Maybe even more high-level:
  Performance of distributed algorithms like replication that are
  built on top of AB}

\paragraph{What problem are you solving, and why is it hard?} 
Tuning of AB to machine characteristics. This is hard because
multicores are complex hierarchical systems. Furthermore, there is a
huge variety of such machines with different characteristics
influencing performance.

@@

\paragraph{How will you go about it?}
Online measurements to parametrize Model \ska evaluation of different
implementations for machine (also combination of message-passing and
shared-memory) \ska pick best fit \ska auto-tune implementation

\paragraph{How will you know and show it works?}
Compare different AB implementations. Show that performance depends on
machine. Show that our evaluation picks the best one (significantly
better than base-line, which is naive or simple tree). Verify
performance benefit for high-level application.

@@

\paragraph{What is your hypothesis?}
Topology matters. We can do better with hybrid models. Automatic tuning achieves good
performance, without programmers having to deal with complex hardware details.
